---
title: 'Developing Data Products: Plotly'
author: "Noluthando Ndlovu"
date: "20 July 2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Violent Crime Rates by US State

Statistics in arrests per *100 000* residents for

- Assault
- Murder
- Rape

Also given is the percentage of the population living in Urban Areas

## Getting the data

```{r echo=TRUE, message=FALSE, warning=FALSE, comment=""}
library(plotly)
library(datasets)
data <- datasets::USArrests
head(data, n = 2)
summary(data)
```

## Is assault correllated with murder?

```{r echo=TRUE, message=FALSE, warning=FALSE, comment=""}
plot_ly(data, x = ~Murder, y = ~Assault,
        type = "scatter", color = ~UrbanPop)
```

## Is rape correllated with murder?

```{r echo=TRUE, message=FALSE, warning=FALSE, comment=""}
plot_ly(data, x = ~Murder, y = ~Rape,
        type = "scatter", color = ~UrbanPop)
```

## Observations

From the previous slide, there a few things we can pick up:
- as the number of assaults increases, the number of murders also increase
- areas with a smaller percentage of people living in urban rates have lower crime rates (both assault and murder)

Nothing obvious arises from the relationship betwwen number of rapes and number of murders.
